Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-04-25 Manuscript/manuscript.Rmd
wip

The distinct patterns of epigenomic marks, binding peaks of different factors, and actively transcribed genes prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries. Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries. Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], [??? Describe other hallmarks of TAD boundaries, with references. And, most importantly, why you are doing your study?]

>>>>

The distinct patterns of chromatin states, active or repressive histone marks, binding peaks of different factors associated with the 3D structures [@Naumova:2010aa; @Hou:2012aa] prompt the use of computational approaches to identify which epigenomic features are most predictive of TAD boundaries. Current methods rely on the use of classification algorithms to draw associations between the spatial relationship of functional genomic elements and regions that include TAD boundaries. Although several useful insights have been made, such as the convergent binding of CTCF [@ong2014ctcf; @ghirlando2016ctcf], [??? Describe other hallmarks of TAD boundaries, with references. And, most importantly, why you are doing your study?]
